\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons

### 2024-12-18 TilingProjectDraft/tilingProject.tex
jotted down some points regarding the non-Fermi liquid

>>>>

\subsection{Nature of the metal near the transition}
Some thoughts about the nature of the metal near the transition:
\begin{itemize}
	\item Typically, there arises some kind of degeneracy close to points of Kondo breakdown. In this model, this presumably happens when each Fermi surface point \(k\) starting from the antinodes begin to decouple from the Kondo cloud; at every such point, the local moment state \(\ket{\sigma_d,n_k=0(2)}\) and the singlet state \(\sum_\sigma \sigma\ket{\sigma_d,-\sigma_k}\) become degenerate.
	\item This also should lead to the orthogonality catastrophe for the local Fermi liquid arising from these \(k-\)points. Overall, these two features can probably be combined together using the observation (-> verify) that the embedded eSIAM is a collection of radial eSIAMs.
	\item With regards to the metal arising from the singular nodal points just before the transition, we can carry out the following calculation. In order to obtain the low-lying excitations, we treat the largest Kondo scattering terms (which turn out to be the ones at and between the nodes) as a perturbation above the bath interaction term, and ignore all other Kondo scattering terms (which are either already irrelevant or much smaller than the ones at the node). Integrating out the impurity dynamics in this fashion should (-> verify) lead to density-density interactions at the node (\(\mathcal{U}n_{k \uparrow} n_{k \downarrow}\) as well as between the nodes (\(\mathcal{U}n_{k \uparrow} n_{{k + Q} \downarrow}\), where \(Q = \left(\pi, \pi\right) \)). The low-lying excitations are therefore described by a Hatsugai-Kohmoto model (HKM).
	\item The emergence of the HKM indicates that the nodal points harbour a non-Fermi liquid. Since the model is exactly solvable, one can try to calculate various diagnostics such as the quasiparticle residue and the self-energy. It is also interesting to note that a similar trick was employed in our 1CK work to obtain the effective theory for the Kondo cloud; there, because of the more democratic nature of the Kondo interaction (in \(k-\)space), the effective theory had all kinds of terms (not just the HKM). That was of course associated with local Fermi liquid behaviour. It appears, therefore, that the selective irrelevance of certain \(k-\)modes on the Fermi surface in terms of Kondo screening transforms the "all-to-all" Kondo cloud theory into the non-Fermi liquid HKM near the transition.
\end{itemize}

\subsection{Formal description of the tiling procedure}
We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian. The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model. The local behaviour of this impurity model should reflect the essential local physics of the lattice model. Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction. We will henceforth refer to this site as the zeroth site. In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.35\textwidth]{particleHoleRelation.pdf}
	\caption{Particle and hole states.}
	\label{fig:particleHoleRelation-pdf}
\end{figure}
\subsection{Renormalisation of the bath correlation term {\it W}}
The bath correlation term \(W\) can undergo renormalisation only via scattering processes arising from itself. Irrespective of whether the state \({\bf q}\) being decoupled is in a particle or hole configuration in the initial many-body state, the propagator \(G = 1/(\omega - H_D)\) of the intermediate excited state is uniform, and equal to 
\begin{equation}\begin{aligned}\label{propagatorW}
	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)
\end{itemize}
